Severe CDI manuscript

### 2022-11-28 paper/paper.qmd
Update ms ext

---
title: "Severe CDI manuscript"
bibliography: references.bib
csl: mbio.csl
fontsize: 12pt
date: last-modified
date-format: medium
toc: true
lof: true
number-sections: false
format: 
  manuscript-pdf:
    keep-tex: true
    include-in-header: header.tex
  #gfm: default
  html: default
author:
  - name: Kelly L. Sovacool
    orcid: 0000-0003-3283-829X
    affiliations:
      - ref: bioinf
  - name: Sarah E. Tomkovich
    affiliations:
      - ref: micro
  - name: Megan L. Coden
    affiliations:
      - ref: mcdb
  - name: Vincent B. Young
    affiliations:
      - ref: micro
      - ref: intmed
  - name: Krishna Rao
    affiliations:
      - ref: intmed
  - name: Patrick D. Schloss
    email: pschloss@umich.edu
    corresponding: true
    orcid: 0000-0002-6935-4275
    affiliations:
      - ref: micro
      - ref: ccmb
affiliations:
  - id: bioinf
    name: Department of Computational Medicine & Bioinformatics, University of Michigan
  - id: micro
    name: Department of Microbiology & Immunology, University of Michigan
  - id: mcdb
    name: Department of Molecular, Cellular, and Developmental Biology, University of Michigan
  - id: intmed
    name: Division of Infectious Diseases, Department of Internal Medicine, University of Michigan
  - id: ccmb
    name: Center for Computational Medicine and Bioinformatics, University of Michigan
abstract: TODO
importance: TODO
keywords: _C. difficile_ infection, supervised machine learning
---

## Introduction

## Results and Discussion

## Conclusions

## Materials and Methods

## References

>>>>

---
title: "Severe CDI manuscript"
bibliography: references.bib
fontsize: 11pt
date: last-modified
date-format: medium
format: 
  manuscript-pdf:
    keep-tex: true
    include-in-header: header.tex
    linenumbers: true
    doublespacing: true
    lof: false
  #gfm: default
  html: default
runningtitle: Predicting Severe _C. difficile_ infections
runningauthor: Sovacool
papertype: Preprint
author:
  - name: Kelly L. Sovacool
    orcid: 0000-0003-3283-829X
    affiliations:
      - ref: bioinf
  - name: Sarah E. Tomkovich
    affiliations:
      - ref: micro
  - name: Megan L. Coden
    affiliations:
      - ref: mcdb
  - name: Vincent B. Young
    affiliations:
      - ref: micro
      - ref: intmed
  - name: Krishna Rao
    affiliations:
      - ref: intmed
  - name: Patrick D. Schloss
    email: pschloss@umich.edu
    corresponding: true
    orcid: 0000-0002-6935-4275
    affiliations:
      - ref: micro
      - ref: ccmb
affiliations:
  - id: bioinf
    name: Department of Computational Medicine & Bioinformatics, University of Michigan
  - id: micro
    name: Department of Microbiology & Immunology, University of Michigan
  - id: mcdb
    name: Department of Molecular, Cellular, and Developmental Biology, University of Michigan
  - id: intmed
    name: Division of Infectious Diseases, Department of Internal Medicine, University of Michigan
  - id: ccmb
    name: Center for Computational Medicine and Bioinformatics, University of Michigan
abstract: TODO
importance: TODO
keywords: _C. difficile_ infection, supervised machine learning
---

# Introduction

# Results

# Discussion

# Materials and Methods

# Acknowledgements
